```latex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, graphicx, hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\title{SHOA-Validate: Calibration, Validation, and Falsification Protocol for the SHOA Model}
\author{Konstantin Fedotov}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We present SHOA-Validate, a comprehensive calibration and validation framework for the SHOA family of models. This protocol provides experimenters with reproducible criteria for verifying or falsifying the core hypotheses of quantum self-healing, learning, and emergent resilience. The framework includes four formal criteria: a Fidelity threshold for restoration, an integral resilience index, a formalized memory law, and a coherent activation criterion. We provide precise definitions, measurement procedures, target values, and the necessary instrumentation for each.
\end{abstract}

\section{Introduction}
The SHOA models (Classic, Neuro, Scoring, Hedge, etc.) require rigorous experimental validation to transition from theoretical constructs to accepted physical laws. SHOA-Validate establishes a standardized, reproducible protocol that enables independent laboratories to test and potentially falsify the predictions of the SHOA framework.

\section{Mathematical Model (Synopsis)}
The core dynamics of a SHOA ensemble are governed by the Lindblad master equation:
\begin{equation}
\frac{d\rho}{dt} = -\frac{i}{\hbar} [\mathcal{H}, \rho] + \sum_i \Gamma \mathcal{D}[\sigma_-^{(i)}]\rho,
\end{equation}
where $\mathcal{D}[L]\rho = L \rho L^\dagger - \frac{1}{2} \{ L^\dagger L, \rho \}$ is the dissipator. The Hamiltonian includes local terms, collective interactions, and a GRAPE-optimized control pulse:
\begin{equation}
\mathcal{H} = \sum_i \frac{\Delta_i}{2} \sigma_z^{(i)} + \sum_{i<j} J_{ij} \vec{\sigma}^{(i)} \cdot \vec{\sigma}^{(j)} + \sum_i \Omega_i(t) \sigma_x^{(i)}.
\end{equation}
This model provides the theoretical foundation for the following validation criteria.

\section{Criteria and Metrics}

\subsection{Fidelity Restoration Threshold (Criterion I)}
\begin{itemize}
    \item \textbf{Definition:} $\langle \psi_{\text{target}} | \rho(t) | \psi_{\text{target}} \rangle > 0.9$
    \item \textbf{What to measure:} The overlap of the ensemble's density matrix with the ideal state after a damage event.
    \item \textbf{Target value:} $> 0.9$.
    \item \textbf{Instrumentation:} Verified via Quantum State Tomography (QST) on platforms with individual readout (NV centers, single quantum dots).
\end{itemize}

\subsection{Integral Resilience Index (Criterion II)}
\begin{itemize}
    \item \textbf{Definition:} $\mathcal{S}_{\text{neuro}} = \frac{1}{T} \int_0^T \left(1 - \frac{\| \rho(t) - \rho_{\text{ideal}} \|}{\| \rho_{\text{ideal}} \|} \right) dt$
    \item \textbf{What to measure:} The average proximity of the ensemble's state to the ideal state over the entire recovery interval.
    \item \textbf{Hypothesis test:} A system with memory (SHOA-Neuro) must show a monotonic increase in $\mathcal{S}_{\text{neuro}}$ from cycle to cycle, in contrast to a static system without Spiked Voting.
\end{itemize}

\subsection{Formalized Memory Law (Criterion III)}
\begin{itemize}
    \item \textbf{Definition:} $K_{\text{eff}}(N) = K_0 \cdot \left(1 - \beta e^{-\lambda N_{\text{recovery}}} \right)$
    \item \textbf{What to measure:} The effective stiffness (or activation threshold) as a function of the number of previous recovery cycles $N_{\text{recovery}}$.
    \item \textbf{Extractable parameters:}
        \begin{itemize}
            \item $\beta$ -- learning amplitude (fraction of the maximum threshold change),
            \item $\lambda$ -- learning rate (saturation constant).
        \end{itemize}
    \item \textbf{Prediction:} For a system with Spiked Voting, $\lambda > 0$; for a control system without it, $\lambda \to 0$.
\end{itemize}

\subsection{Coherent Activation Criterion (Criterion IV)}
\begin{itemize}
    \item \textbf{Definition:} $M_{\text{spin}} > M_{\text{crit}}$ and simultaneously $f_{\text{cure}} > \gamma T$
    \item \textbf{What to measure:} The total spin polarization $M_{\text{spin}}$ of the ensemble and the power of the control pulse $f_{\text{cure}}$.
    \item \textbf{Significance:} Recovery is triggered not merely by the presence of energy, but only by a coherent, ordered (spin-polarized) stimulus. This criterion excludes trivial thermal annealing as the mechanism.
\end{itemize}

\section{Conclusion}
SHOA-Validate provides experimenters with a reproducible protocol for the falsification or confirmation of the SHOA model. The four criteria outlined here transform the theoretical framework into a testable scientific theory, ready for independent laboratory verification.

\end{document}
