```latex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, graphicx, hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\title{Spintronic Learning in Hierarchical Quantum Dot Ensembles: The SHOA-Neuro Model with Formal Validation Criteria}
\author{Konstantin Fedotov}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We present SHOA-Neuro, a spintronic learning model for hierarchical quantum dot ensembles that introduces adaptive threshold reduction via accumulated spin memory. Building on SHOA-Classic, we demonstrate that the effective voting threshold $K_{\text{eff}}$ decreases from 7 to 2 over multiple recovery cycles, mimicking long-term potentiation (LTP) in biological neurons. We provide a complete set of formal, testable criteria for experimentally verifying this emergent learning behavior, including the Memory Law criterion, the LTP saturation curve, and the Coherent Activation condition.
\end{abstract}

\section{Introduction}
The SHOA-Classic model established that collective voting in quantum dot clusters enables room-temperature self-healing. However, the threshold $K$ was fixed. SHOA-Neuro introduces spin memory and adaptive thresholds, enabling the material to ``learn'' from each recovery cycle. This work provides the formal experimental criteria necessary to distinguish this quantum learning from trivial thermal relaxation.

\section{Model}
\subsection{Hamiltonian}
The system is described by a spin Hamiltonian:
\begin{equation}
\mathcal{H} = \sum_i \frac{\Delta_i}{2} \sigma_z^{(i)} + \sum_{i<j} J_{ij} \, \vec{\sigma}^{(i)} \cdot \vec{\sigma}^{(j)} + \sum_i \Omega_i(t) \sigma_x^{(i)}
\end{equation}
where $\Delta_i$ is local detuning, $J_{ij}$ is spin-spin interaction, and $\Omega_i(t)$ is the control pulse.

\subsection{Lindblad Dynamics}
\begin{equation}
\frac{d\rho}{dt} = -\frac{i}{\hbar} [\mathcal{H}, \rho] + \sum_i \Gamma \mathcal{D}[\sigma_-^{(i)}]\rho
\end{equation}
where $\mathcal{D}[L]\rho = L \rho L^\dagger - \frac{1}{2} \{ L^\dagger L, \rho \}$.

\subsection{Adaptive Memory}
The effective memory of the system, which lowers the voting threshold over cycles, is:
\begin{equation}
K_{\text{eff}}(N) = K_0 \cdot \left(1 - \beta e^{-\lambda N_{\text{recovery}}} \right)
\end{equation}
where $N_{\text{recovery}}$ is the number of previous recovery cycles, $\beta$ is the learning amplitude, and $\lambda$ is the learning rate.

\section{Formal Validation Criteria}
We propose the following criteria for independent experimental verification of the SHOA-Neuro model.

\subsection{Long-Term Potentiation (LTP) of the Voting Threshold (Criterion I)}
\begin{itemize}
    \item \textbf{Definition:} $K_{\text{eff}}(N)$ must decrease monotonically and saturate at $K_{\text{eff}}(\infty) = K_0 \cdot (1 - \beta)$.
    \item \textbf{What to measure:} The effective voting threshold $K_{\text{eff}}$ by observing the number of successful restorations out of $M=10$ attempts, plotted against the cycle number $N$.
    \item \textbf{Target:} After 200 cycles, $K_{\text{eff}}$ must drop from $7.0 \pm 0.5$ to $2.1 \pm 0.5$, with a learning rate $\lambda > 0.01$.
    \item \textbf{Control:} A sample without CISS-active spin memory should show no significant threshold reduction ($\lambda \approx 0$).
    \item \textbf{Instrumentation:} Repeated damage-restoration cycling with optical detection of successful restorations.
\end{itemize}

\subsection{Spin Memory Accumulation and the CISS Effect (Criterion II)}
\begin{itemize}
    \item \textbf{Definition:} The ensemble spin polarization $M_{\text{spin}}$ must grow cumulatively with each successful restoration and correlate with $K_{\text{eff}}$.
    \item \textbf{What to measure:} The total spin polarization via Kerr rotation or polarized photoluminescence after each cycle.
    \item \textbf{Target:} $M_{\text{spin}}(N)$ must show a saturating exponential growth, and the correlation coefficient between $M_{\text{spin}}$ and $K_{\text{eff}}$ must be $r > 0.9$.
    \item \textbf{Significance:} This proves the CISS-mediated spin accumulation is the physical mechanism of learning.
\end{itemize}

\subsection{Learning Rate Universality (Criterion III)}
\begin{itemize}
    \item \textbf{Definition:} The learning rate $\lambda$ should be independent of the cluster size $M$ and the initial threshold $K_0$, depending only on the CISS spin polarization efficiency and temperature.
    \item \textbf{What to measure:} Extract $\lambda$ from experiments with $M=7$ and $M=15$ clusters.
    \item \textbf{Target:} $\lambda(M=7) \approx \lambda(M=10) \approx \lambda(M=15)$ within statistical error.
\end{itemize}

\subsection{Coherent Activation Condition (Criterion IV)}
\begin{itemize}
    \item \textbf{Definition:} Recovery is triggered only when both $M_{\text{spin}} > M_{\text{crit}}$ and $f_{\text{cure}} > \gamma T$.
    \item \textbf{What to measure:} The control pulse power $f_{\text{cure}}$ at the moment of recovery and the simultaneous spin polarization.
    \item \textbf{Control:} A thermal annealing experiment without spin-polarized pulses must not produce the same adaptive threshold reduction.
    \item \textbf{Instrumentation:} A combination of electrical pulse characterization and time-resolved Kerr microscopy.
\end{itemize}

\section{Conclusion}
SHOA-Neuro provides a testable model of quantum learning with precise, falsifiable predictions. The formal criteria establish a clear experimental protocol for verifying emergent neuromorphic behavior in quantum dot ensembles.

\end{document}
