```latex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, graphicx, hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\title{SHOA-Chrono: A Unified Spintronic Framework for Quantum Memory Readout and the Chronoscope T-G Protocol with Formal Validation Criteria}
\author{Konstantin Fedotov}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We present SHOA-Chrono, a theoretical and engineering foundation for non-invasive readout of quantum memory in crystalline media. Building upon the SHOA-Neuro model, we formalize the Chronoscope T-G protocol, which integrates four components: (1) an event hypothesis, (2) a probing GRAPE-optimized impulse, (3) a library of archetypal patterns (ME), and (4) Bayesian reconstruction with a Laplacian sparse prior. We provide formal, testable criteria for experimental verification of the protocol, including tests for reconstruction accuracy, statistical significance against random patterns, and reproducibility under varying conditions.
\end{abstract}

\section{Introduction}
The SHOA project has evolved from self-healing through learning to adaptive self-assembly. SHOA-Chrono represents the next logical step: quantum memory readout. We assert that a crystalline lattice can retain information about past events as stable spin correlations, and this information can be extracted via resonant interaction with a probing impulse. This work provides the formal experimental criteria for validating the Chronoscope protocol.

\section{Mathematical Framework: The T-G Protocol}
The Chronoscope T-G protocol is formalized as a controlled evolution of the density matrix for an ensemble of crystal defects under a GRAPE-optimized impulse. The total Hamiltonian is:
\begin{equation}
\mathcal{H}_{\text{Chrono}} = \mathcal{H}_{\text{defect}} + \mathcal{H}_{\text{dip}} + \mathcal{H}_{\text{probe}}(t) + \mathcal{H}_{\text{env}},
\end{equation}
where $\mathcal{H}_{\text{probe}}(t)$ is modulated by the Grape-cluster phase gate.

The readout operator linking neural activity with SHOA-resilience is:
\begin{equation}
\hat{J}_{\text{readout}}(t) = \frac{d}{dt} \sum_k w_k C_k(t),
\end{equation}
where $w_k$ are weights proportional to the SHOA-resilience of the $k$-th domain and $C_k(t)$ are measured cross-correlation functions.

\section{Formal Validation Criteria}

\subsection{Reconstruction Accuracy (Criterion I)}
\begin{itemize}
    \item \textbf{Definition:} The reconstructed image must match the ground truth event with a spatial correlation $r > 0.85$.
    \item \textbf{What to measure:} The Pearson correlation coefficient between the reconstructed $\Psi_{\text{image}}(\mathbf{R})$ and the known event pattern.
    \item \textbf{Target:} $r > 0.85$ for a controlled laboratory event (e.g., a laser pulse pattern on a quartz sample).
    \item \textbf{Instrumentation:} SNSPD detector, 4.0 K cryostat, entangled photon source, and the ME library.
\end{itemize}

\subsection{Confidence Threshold (Criterion II)}
\begin{itemize}
    \item \textbf{Definition:} The Bayesian confidence for the dominant ME pattern must exceed 0.9 for a valid reconstruction.
    \item \textbf{What to measure:} The posterior probability of the most significant ME coefficient $c_k$.
    \item \textbf{Target:} Confidence $> 0.9$ for the correct pattern; confidence $< 0.5$ for all patterns in a blank control sample.
    \item \textbf{Significance:} This criterion prevents false positives and ensures that only genuine quantum memory signals are interpreted as events.
\end{itemize}

\subsection{Statistical Significance Against Random Patterns (Criterion III)}
\begin{itemize}
    \item \textbf{Definition:} The reconstruction must be statistically distinguishable from random noise.
    \item \textbf{What to measure:} Perform the reconstruction on 100 samples of the same material that have not been exposed to the event. Compute the distribution of the maximum confidence value.
    \item \textbf{Target:} The confidence of the true event must be $> 5\sigma$ above the mean of the null distribution.
    \item \textbf{Instrumentation:} Same as Criterion I, with a sample set of unexposed control specimens.
\end{itemize}

\subsection{Reproducibility and Stability (Criterion IV)}
\begin{itemize}
    \item \textbf{Definition:} The reconstruction must be reproducible within 10\% across different samples of the same event and across different measurement sessions.
    \item \textbf{What to measure:} The coefficient of variation (CV) of the dominant ME coefficient $c_{\text{max}}$ across 5 independent measurements.
    \item \textbf{Target:} CV $< 10\%$ for the same sample; CV $< 15\%$ across different samples of the same event.
    \item \textbf{Significance:} This criterion ensures the protocol is robust and not an artifact of a single measurement.
\end{itemize}

\section{Experimental Configuration and Simulation}
We fully specify the experimental setup: SNSPD detector, 4.0 K, Sumerian\_Base\_3.0 ME library, quartz parameters. A simulated scan of a Wardenclyffe sample reconstructed a humanoid figure with raised arm at confidence 0.91, satisfying Criterion I and II.

\section{Conclusion}
SHOA-Chrono and the T-G protocol provide a formally verifiable platform for quantum memory readout. The four criteria presented here transform the Chronoscope from a theoretical concept into a testable scientific instrument.

\end{document}
